Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-29 numerical-conduction.tex
working on thermal conductiom sections.

>>>>

Enzo implements the equations of isotropic heat conduction in a manner
similar to that of \citet{2007ApJ...664..135P}, where we model the
flux of isotropic heat transport:

\begin{equation}
\mathbb{F} = -\kappa_{sp} \nabla T
\end{equation}

Where $\kappa_{sp}$ is the Spitzer conduction coefficient, $4.6 \times 10^{-7}$~T$^{5/2}$ erg
s$^{-1}$~cm$^{-1}$~K$^{-1}$ \citep{1962pfig.book.....S}, and using a
value for the Coulomb logarithm, $\log \Lambda = 37.8$, that is
appropriate for the intracluster medium \citep{1988xrec.book.....S}.
It is quite possible that the local heat flux can become unphysical in
the high-temperature, low-density cluster regime when using this
formulation; thus, we take into account the saturation of the heat
flux at a maximum level of

\begin{equation}
j_{sat} \simeq 0.4 n_e k_b T \left( \frac{2 k_b T}{\pi m_e} \right)^{1/2}
\end{equation}

\citep{1977ApJ...211..135C}, and to ensure a smooth transition between
the Spitzer regime and the saturated regime we define an effective
conductivity using the formalism of \citet{1988xrec.book.....S}

\begin{equation}
\kappa_{eff} = \frac{\kappa_{sp}}{1 + 4.2 \lambda_e / \ell_T} \; ,
\end{equation}

where $\lambda_e$ is the electron mean free path and $\ell_T \equiv T
/ |\nabla T|$ is the characteristic length scale of the local
temperature gradient.

It is important to note that the conductivity can be strongly affected
by the presence of magnetic fields, which may strongly suppress heat
flow.  The strength and confuction of magnetic fields in the
intracluster medium is poorly understood, and it is unclear to what
extent these magnetic fields will suppress conduction.  For the
purposes of the work described in this paper, we assume that the
conductivity of the plasma can be described in terms of an effective
conductivity, which can be expressed as a fraction f$_{Sp}$ of the
Spitzer conductivity (where f$_{Sp} \leq 1.0$ are considered physical
values).

### 2013-01-29 overview.tex
working on thermal conductiom sections.

>>>>

\subsubsection{Magnetohydrodynamics}

\subsubsection{Radiation transport: ray-casting}

\subsubsection{Radiation transport: moment method}

\subsubsection{Thermal conduction}

Enzo implements the equations of isotropic heat conduction in a manner
similar to that of \citet{2007ApJ...664..135P}, where we model the
flux of isotropic heat transport:

\begin{equation}
\mathbb{F} = -\kappa_{sp} \nabla T
\end{equation}

Where $\kappa_{sp}$ is the Spitzer conduction coefficient
\citep{1962pfig.book.....S}.  Saturation of the heat flux in
high-temperature, low-density regimes (such as the intracluster medium
in galaxy clusters) is taken into account.  Thermal conduction in a
plasma can be strongly affected by the presence of magnetic field
lines, which may strongly suppress heat flow perpendicular to the
magnetic field.  In that case, we allow for heat transport only along
the magnetic field lines in simulations that include this physics, as follows:

\begin{equation}
\mathbb{F} = -\kappa_{sp} \^{b} (\^{b} \cdot \nabla T)
\end{equation}

Where $\^{b}$ is the unit vector denoting the direction of the
magnetic field.  In both the isotropic and anisotropic limits, we
assume that conductivity can be suppressed relative to the ideal
Spitzer conductivity, and express this as a constant multiplier.
